On the error performance of the $A_n$ lattices

### 2011-11-12 paper.tex
Fixed some notational inconsistencies.  This would have made things hard to follow.  This really needs another read, and I need to fix the simulations.

The \emph{root lattices} $A_n$, $D_n$, $E_6$, $E_7$ and $E_8$ have attracted particular attention as structured codes for the AWGN channel~\cite{SPLAG}. The highly symmetric structure of these lattices provides the grounds for extremely efficient decoding algorithms.  In this paper we consider codes constructed from the root lattice $A_n$ and derive formulae for accurately predicting the performance of these codes.  This is achieved by deriving formulae for the \emph{moments} of the \emph{Voronoi cell} of $A_n$.  Conway and Sloane suggested this approach to compute the quantizing constants (second order moments) of the root lattices,~\cite{Conway1982VoronoiRegions}.  In this paper we extend their technique to compute the moments of any order for $A_n$.

@@

This paper is organised as follows.  In Section~\ref{sec:latt-latt-codes} we give a brief overview of lattices and codes constructed from them, i.e., \emph{lattice codes}.  We describe lattice decoding and show how the probability of coding error can be expressed in terms of the moments of the \emph{Voronoi cell} of the lattice used.  Section~\ref{sec:main-result} states the main result (without proof), which gives recursive formula to compute the moments of the Voronoi cell of $A_n$.  Section~\ref{sec:lattice-a_n} describes the lattice $A_n$ and some of its properties.  An important property for our purposes is that the Voronoi cell of $A_n$ is precisely the projection of a $n+1$-dimensional hypercube orthogonal to one of its vertices~\cite{McKilliam2009CoxeterLattices,McKilliam2010thesis}.
 %This result was previously known~\cite{McKilliam2009CoxeterLattices,McKilliam2010thesis}.  The proof is short and we give it again here so that this paper is self contained.
In Section~\ref{sec:integr-funct-over} we use this property to show how integrals over the Voronoi cell of $A_n$ can be expressed as integrals over the $n$-dimensional hypercube. These integrals are solvable and we use them to obtain the moments of the Voronoi cell in Section~\ref{sec:powers-eucl-norm}.  In Section~\ref{sec:results-simulations} we plot the probability of error versus signal to noise ratio for codes constructed from the lattices $A_1 \simeq \ints$, $A_2$, $A_3 \simeq D_3$ and $A_4$.  We also plot the results of Monte-Carlo simulations that support our analytical results.
%An advantage of the analytical results is that the probability of error can calculated at high SNR, when the probabilty of error is small.  This is in contrast to Monte-Carlo simulations that are computationally infeasible at when the probability of error is small.  We display the performance of these lattice codes

@@

A \term{lattice}\index{lattice}, $\Lambda$, is a countable subset of points in $\reals^m$ such that
\[
   \Lambda = \{\xbf = \Bbf\ubf \mid \ubf \in \ints^n \}
 \]
 for a certain rank-$n$ $m \times n$ matrix $\Bbf$ of real elements, called the \term{generator matrix} or \term{basis matrix} or simply generator or basis. Since the generator matrix has rank $n$, the lattice $\Lambda$ is termed $n$-dimensional. If the generator is square, i.e. $m = n$, then the lattice points span $\reals^n$ and we say that the lattice is \term{full rank}. If $\Bbf$ has more rows than columns, i.e. $m > n$, then the lattice points lie in a $n$-dimensional subspace of $\reals^m$. For any lattice $\Lambda$ with an $m \times n$ generator matrix, we also define $\mathcal{S}_{\Lambda}$ to be the sub-space spanned by the columns of the generator matrix. The set of $n$-tuples of integers $\ints^n$ is a lattice (with the identity matrix as the generator) and we call this the~\emph{integer lattice}.

@@

Let $\calX$ be a lattice code constructed from a lattice $\Lambda$.  Assuming that each codeword $\xbf \in \calX$ has an equal probability of being transmitted and that the receiver employs lattice decoding, then the average probability of correct decoding in the AWGN channel is
%\footnote{In order to approach capacity Erez and Zamir~\cite{Erex2004_lattice_decoding} employ a uniform dither and also a minimum mean square error scaling parameter $\alpha$ (the so called \emph{modulo-lattice additive noise channel}).  A result of this is that that observed noise distribution is no longer Gaussian. However, for large signal to noise ratio $\alpha \approx 1$ and the observed noise is very close to Gaussian.  In this case~\eqref{eq:PEgaussian} is a reasonable approximation.}
\begin{align}
P_C &\leq P_C(\Lambda) = \lim_{\abs{\calX}\rightarrow \infty}
 \frac{1}{\abs{\calX}} \sum_{\xbf\in \calX} \prob( \xbf + \wbf \in
\vor(\Lambda) + \xbf )  \nonumber \\
&= \prob(\xbf \in \vor(\Lambda) ) \nonumber \\
&=   \frac{1}{(\sqrt{2\pi}\sigma)^n} \int_{\vor(\Lambda)}
e^{-\|\xbf\|^2 / 2\sigma^2 } d\xbf. \label{eq:PEgaussian}
\end{align}
The probability of error is $P_E \leq 1 - P_C(\Lambda)$, where the upper bound is asymptotically tight for large constellations (the proportion of the codewords near the boundary of the shaping region becomes small).  By expanding $e^x = 1  + x + \frac{x^2}{2} + \dots$ we obtain
\begin{align}
P_C(\Lambda)  &= \frac{1}{(\sqrt{2\pi}\sigma)^n}\int_{\vor(\Lambda)} 1
- \frac{\|\xbf\|^2}{2\sigma^2} + \frac{\left(\|\xbf\|^2\right)^2}{
4\sigma^42!} - \dots d\xbf \nonumber \\
&= \frac{1}{(\sqrt{2\pi}\sigma)^n} \sum_{m=0}^\infty
\frac{(-1)^m}{2^m\sigma^{2m}m!} \int_{\vor(\Lambda)} \|\xbf\|^{2m}
d\xbf.  \label{eq:summomentproberror}
\end{align}
So, to obtain arbitrarily accurate approximations to the probability of error it is enough to know the values of $\int_{\vor(\Lambda)} \|\xbf\|^{2m} d\xbf$ for $m=1,2\dots$ for some sufficiently large $m$.  The number of terms required will increase as the noise variance gets smaller.  This implies that the bound with a fixed number of terms is not asymptotically tight but is very accurate up to a finite signal-to-noise ratio.

@@

The Voronoi cell of $A_n$ is closely related to the $n+1$ dimensional hypercube $\vor(\ints^{n+1})$ as the next theorem will show.  This result has appeared previously~\cite{McKilliam2009CoxeterLattices,McKilliam2010thesis}, but we repeat it here so that this paper is self contained.  We denote by
\[
\Qbf = \Ibf - \frac{\onebf\onebf^\prime}{n+1}
\]
the projection matrix orthogonal to $\onebf$ (i.e. into $H$) where $\Ibf$ is the $n+1$ by $n+1$ identity matrix.  Given a set $S$ of vectors from $\reals^{n+1}$ we write $\Qbf S$  to denote the set with elements $\Qbf \sbf$ for all $\sbf \in S$, i.e. the set containing the projection of the vectors from $S$.

\begin{lemma} \label{lem:QVorZnsubsetVorAn}
The projection of $\vor(\ints^{n+1})$ into H is a subset of $\vor(A_{n})$.  That is,
\[
\Qbf\vor(\ints^{n+1}) \subseteq \vor(A_{n}).
\]
\end{lemma}
\begin{IEEEproof}
Let $\ybf \in \vor(\ints^{n+1})$.  Decompose $\ybf$ into orthogonal components so that $\ybf = \Qbf \ybf + t \onebf$ for some $t \in \reals$.  Then $\Qbf\ybf \in \Qbf\vor(\ints^{n+1})$.  Assume that $\Qbf\ybf \notin \vor(A_n)$.  Then there exists some $\xbf \in A_n$ such that
\begin{align*}
\|\xbf - \Qbf\ybf\|^2 < \|\zerobf - \Qbf\ybf\|^2 & \Rightarrow \|\xbf - \ybf + t\onebf\|^2 < \|\ybf - t\onebf\|^2 \\
%& \Rightarrow \|\xbf - \ybf\|^2 + 2t(\xbf - \ybf)'\onebf + t^2\|\onebf\|^2 < \|\ybf\|^2 - 2t\ybf'\onebf + t^2\|\onebf\|^2 \\
& \Rightarrow \|\xbf - \ybf\|^2 + 2t\xbf'\onebf < \|\ybf\|^2.
\end{align*}
By definition \eqref{eq:An_sub_Zn} $\xbf'\onebf = 0$ so $\|\xbf - \ybf\|^2 < \|\ybf\|^2$.  This violates that $\ybf \in \vor(\ints^{n+1})$ and hence $\Qbf\ybf \in \vor(A_n)$.\footnote{This proof can be generalised to show that for any lattice $L$ and hyperplane $P$ such that $P\cap L$ is also a lattice it is true that $p\vor(L) \subseteq \vor(L \cap P)$ where $p$ indicates the orthogonal projection into $P$~\cite[Lemma~2.1]{McKilliam2010thesis}.}
\end{IEEEproof}

\begin{theorem}  \label{thm:VorAn=QVorZn1}
The projection of $\vor(\ints^{n+1})$ into H is equal to $\vor(A_{n})$. That is,
\[
\vor(A_n) = \Qbf\vor(\ints^{n+1}).
\]
\end{theorem}
\begin{proof}
The $n$-volume of $\vor(A_n)$ is given $\sqrt{n + 1}$.  From Berger~et.~al.~\cite[Theorem 1.1]{Burger1996} we find that the $n$-volume of the projected hypercube $\Qbf\vor(\ints^{n+1})$ is equal to $\sqrt{n + 1}$ also. It follows from Lemma~\ref{lem:QVorZnsubsetVorAn} that $\Qbf\vor(\ints^{n+1}) \subseteq \vor(A_n)$, so, because the volumes are the same, and because $\vor(A_n)$ and $\Qbf\vor(\ints^{n+1})$ are polytopes, we have $\vor(A_n) = \Qbf\vor(\ints^{n+1})$.
\end{proof}

@@

We can make further simplifications.  Letting $t = x_1 - x_2$ and $y = x_1 + 1/2$ and changing variables gives
\[
n \sqrt{n+1} \int^{1}_{0} \int^{y}_{0}  \int^{y - 1/2}_{y - t - 1/2} \cdots \int^{y-1/2}_{y-t-1/2} \frac{f(\Qbf\xbf )}{1 - t}  dx_{n+1} \, \dots \, dx_3 \, dt \, dy,
\]
and letting $w_{i-2} = x_i - y + 1/2 + t$ for $i = 3,\dots,n+1$ gives
\begin{equation}\label{eq:intwewilluse}
n \sqrt{n+1} \int^{1}_{0} \int^{y}_{0}  \int^{t}_{0} \cdots \int^{t}_{0} \frac{f(\Qbf\xbf )}{1 - t}  dw_{n-1} \, \dots \, dw_1 \, dt \, dy.
\end{equation}
Observe that $\xbf = \wbf + (y - t - \nicefrac{1}{2})\onebf$ where $\wbf$ is the column vector $[t, 0, w_1, w_2, \dots, w_{n-1}]^\prime$.  Projecting orthogonal to $\onebf$ gives $\Qbf\xbf = \Qbf \wbf$.  Interestingly $\wbf$ does not contain $y$ so the term inside the integral does not depend on $y$.  This is the integral we will use to compute the moments of $A_n$.

@@

We now derive expressions for the $C_n(m)$.  Setting $f(\Qbf\xbf) = \left(\|\Qbf\wbf\|^{2}\right)^m$ in~\eqref{eq:intwewilluse} we obtain,
\[
\frac{C_m(n)}{n\sqrt{n+1}} = \int_0^1 \int_0^y \int_0^t \cdots \int_0^t \frac{\left(\|\Qbf\wbf\|^2\right)^m}{1 - t} \,dw_{n-1} \, \dots \, dw_1 \, dt \, dy.
\]
Now $\|\Qbf\wbf\|^2 = \|\wbf\|^2 - \frac{1}{n+1}(\wbf^\prime \onebf)^2$ and recalling that $\wbf = [t,0,w_1,\dots,w_{n-1}]'$ we can write
\begin{align*}
\|\Qbf\wbf\|^2 &= \|\wbf\|^2 - \frac{1}{n+1}(\wbf^\prime \onebf)^2 \\
&= t^2 + \sum_{i=1}^{n+1}w_i^2 - \frac{1}{n+1}\left( t + \sum_{i=1}^{n+1}w_i \right)^2 \\
&= t^2 + \sum_{i=1}^{n+1}w_i^2 - \frac{1}{n+1}\left( t^2 + 2 t \sum_{i=1}^{n+1}w_i + \left(\sum_{i=1}^{n+1}w_i \right)^2 \right)\\
&= c + d,
\end{align*}
say, where
\[
c = \left(\frac{n}{n+1} \right) t^2,\qquad \text{and} \qquad d = A - \frac{2t}{n+1}B - \frac{1}{n+1}B^2,
\]
and where,
\[
 A = \sum_{i=1}^{n-1}w_i^2 \qquad \text{and} \qquad B = \sum_{i=1}^{n-1}w_i.
\]
Now,
\[
 \frac{C_m(n)}{n\sqrt{n+1}} =  \int_0^1 \int_0^y \int_0^t \cdots \int_0^t \frac{(c+d)^m}{1 - t} \,dw_{n-1} \, \dots \, dw_1 \, dt \, dy,
\]
and by expanding the binomial $(c+d)^m$ we get
\[
\frac{C_m(n)}{n\sqrt{n+1}} =  \int_0^1 \int_0^y \frac{1}{1 - t}\sum_{k=0}^{m}\binom{m}{k} c^{m-k} \int_0^t \cdots \int_0^t \, d^{k} \,dw_{n-1} \, \dots \, dw_1 \, dt \, dy.
\]
Expanding $d^k$ as a trinomial gives
\begin{align*}
d^k &= \sum_{k_1+k_2+k_3=k} \frac{k! A^{k_1} B^{2k_3 + k_2}}{k_1! k_2! k_3!} \left(\frac{-1}{n+1}\right)^{k_2+k_3}2^{k_2}t^{k_2}  \\
&=  \sum_{a=0}^k\sum_{b=0}^{k-a} \frac{k!  A^{a} B^{2k - 2a - b}}{a! b! (k-a-b)!} \left(\frac{-1}{n+1}\right)^{k - a}2^{b}t^{b}
\end{align*}
where the second line follows by setting $k_1 = a$, $k_2 = b$ and $k_3 = k - a - b$.  In Appendix~\ref{sec:mult-type-integr} we show that the integral of $A^{a} B^{2k - 2a - b}$ over $w_1,\dots w_{n-1}$ is
\[
\int_0^t \cdots \int_0^t A^{a} B^{2k-2a-b} dw_{n-1} \, \dots \, dw_1 = t^{n-1+2k - b} G(n-1,a,2k - 2a - b).
\]
where $G(n,k,m)$ satisfies the recursion given by~\eqref{eq:theGrecursion}.  So, let $D$ satisfy
\begin{align*}
D &= t^{1 - n - 2k}\int_0^t \cdots \int_0^t d^k dw_{n-1} \, \dots \, dw_1 \\
&= \sum_{a=0}^k\sum_{b=0}^{k-a} \frac{2^{b} k!G(n-1,a,2k - 2a - b)}{a! b! (k-a-b)!} \left(\frac{-1}{n+1}\right)^{k - a}.
\end{align*}
Now $c^{m-k} = \left(\frac{n}{n+1} \right)^{m-k} t^{2(m-k)}$ and
\begin{align*}
\frac{C_m(n)}{n\sqrt{n+1}} &= \sum_{k=0}^{m} \binom{m}{k} \left(\frac{n}{n+1} \right)^{m-k} D \int_0^1 \int_0^y \frac{t^{n - 1 + 2m}}{1 - t} \, dt \, dy. \\
&= \frac{1}{n+2m} \sum_{k=0}^{m} \binom{m}{k} \left(\frac{n}{n+1} \right)^{m-k} D.
\end{align*}
This expression is equivalent to that from~(\ref{eq:theCmformula}).

>>>>

The \emph{root lattices} $A_n$, $D_n$, $E_6$, $E_7$ and $E_8$ have attracted particular attention as structured codes for the AWGN channel~\cite{SPLAG}. The highly symmetric structure of these lattices provides the grounds for extremely efficient decoding algorithms\cite{,Conway1982FastQuantDec,McKilliam2009CoxeterLattices,McKilliam2008}.  In this paper we consider codes constructed from the root lattice $A_n$ and derive formulae for accurately predicting the performance of these codes.  This is achieved by deriving formulae for the \emph{moments} of the \emph{Voronoi cell} of $A_n$.  Conway and Sloane suggested this approach to compute the quantizing constants (second order moments) of the root lattices,~\cite{Conway1982VoronoiRegions}.  In this paper we extend their technique to compute the moments of any order for $A_n$.

@@

This paper is organised as follows.  In Section~\ref{sec:latt-latt-codes} we give a brief overview of lattices and codes constructed from them, i.e., \emph{lattice codes}.  We describe lattice decoding and show how the probability of coding error can be expressed in terms of the moments of the \emph{Voronoi cell} of the lattice used.  Section~\ref{sec:main-result} states the main result (without proof), which gives recursive formula to compute the moments of the Voronoi cell of $A_n$.  Section~\ref{sec:lattice-a_n} describes the lattice $A_n$ and some of its properties.  An important property for our purposes is that the Voronoi cell of $A_n$ is precisely the projection of a $n+1$-dimensional hypercube orthogonal to one of its vertices~\cite{McKilliam2009CoxeterLattices,McKilliam2010thesis}.
 %This result was previously known~\cite{McKilliam2009CoxeterLattices,McKilliam2010thesis}.  The proof is short and we give it again here so that this paper is self contained.
In Section~\ref{sec:integr-funct-over} we use this property to show how integrals over the Voronoi cell of $A_n$ can be expressed as integrals over the $n$-dimensional hypercube. These integrals are solvable and we use them to obtain the moments of the Voronoi cell in Section~\ref{sec:powers-eucl-norm}.  In Section~\ref{sec:results-simulations} we plot the probability of error versus signal to noise ratio for codes constructed from the lattices $A_1 \simeq \ints$, $A_2$, $A_3 \simeq D_3$, $A_4$ and $A_5$.  We also plot the results of Monte-Carlo simulations that support our analytical results.
%An advantage of the analytical results is that the probability of error can calculated at high SNR, when the probabilty of error is small.  This is in contrast to Monte-Carlo simulations that are computationally infeasible at when the probability of error is small.  We display the performance of these lattice codes

@@

A \term{lattice}\index{lattice}, $\Lambda$, is a discrete subset of points in $\reals^m$ such that
\[
   \Lambda = \{\xbf = \Bbf\ubf \mid \ubf \in \ints^n \}
 \]
 where $\Bbf \in \reals^{m \times n}$ is an $m \times n$ matrix of rank $n$, called the \term{generator matrix} or \term{basis matrix} or simply generator or basis. Since the generator matrix has rank $n$, the lattice $\Lambda$ is termed $n$-dimensional. If the generator is square, i.e. $m = n$, then the lattice points span $\reals^n$ and we say that the lattice is \term{full rank}. If $\Bbf$ has more rows than columns, i.e. $m > n$, then the lattice points lie in a $n$-dimensional subspace of $\reals^m$. For any lattice $\Lambda$ with an $m \times n$ generator matrix, we define $\mathcal{S}_{\Lambda}$ to be the sub-space spanned by the columns of the generator matrix. The set of $n$-tuples of integers $\ints^n$ is a lattice (with the identity matrix as the generator) and we call this the~\emph{integer lattice}.

@@

Let $\calX$ be a lattice code constructed from a lattice $\Lambda$.  Assuming that each codeword $\xbf \in \calX$ has an equal probability of being transmitted and that the receiver employs lattice decoding, then the average probability of correct decoding in the AWGN channel is
%\footnote{In order to approach capacity Erez and Zamir~\cite{Erex2004_lattice_decoding} employ a uniform dither and also a minimum mean square error scaling parameter $\alpha$ (the so called \emph{modulo-lattice additive noise channel}).  A result of this is that that observed noise distribution is no longer Gaussian. However, for large signal to noise ratio $\alpha \approx 1$ and the observed noise is very close to Gaussian.  In this case~\eqref{eq:PEgaussian} is a reasonable approximation.}
\begin{align}
P_C &\leq P_C(\Lambda) = \lim_{\abs{\calX}\rightarrow \infty}
 \frac{1}{\abs{\calX}} \sum_{\xbf\in \calX} \prob( \xbf + \wbf \in
\vor(\Lambda) + \xbf )  \nonumber \\
&= \prob(\xbf \in \vor(\Lambda) ) \nonumber \\
&=   \frac{1}{(\sqrt{2\pi}\sigma)^n} \int_{\vor(\Lambda)}
e^{-\|\xbf\|^2 / 2\sigma^2 } d\xbf. \label{eq:PEgaussian}
\end{align}
The probability of error is $P_E \leq 1 - P_C(\Lambda)$, where the upper bound is asymptotically tight for large constellations (the proportion of the codewords near the boundary of the shaping region becomes small).  By expanding $e^x = 1  + x + \frac{x^2}{2} + \dots$ according to its MacLauren series we obtain
\begin{align}
P_C(\Lambda)  &= \frac{1}{(\sqrt{2\pi}\sigma)^n}\int_{\vor(\Lambda)} 1
- \frac{\|\xbf\|^2}{2\sigma^2} + \frac{\left(\|\xbf\|^2\right)^2}{
4\sigma^42!} - \dots d\xbf \nonumber \\
&= \frac{1}{(\sqrt{2\pi}\sigma)^n} \sum_{m=0}^\infty
\frac{(-1)^m}{2^m\sigma^{2m}m!} \int_{\vor(\Lambda)} \|\xbf\|^{2m}
d\xbf.  \label{eq:summomentproberror}
\end{align}
So, to obtain arbitrarily accurate approximations to the probability of error it is enough to know the values of $\int_{\vor(\Lambda)} \|\xbf\|^{2m} d\xbf$ for $m=1,2\dots$ for some sufficiently large $m$.  The number of terms required will increase as the noise variance gets smaller.  This implies that the bound with a fixed number of terms is not asymptotically tight but is very accurate up to a finite signal-to-noise ratio.

@@

The Voronoi cell of $A_n$ is closely related to the $n+1$ dimensional hypercube $\vor(\ints^{n+1})$ as the next theorem will show.  This result has appeared previously~\cite{McKilliam2009CoxeterLattices,McKilliam2010thesis}, but we repeat it here so that this paper is self contained.  We denote by
\[
\Qbf = \Ibf - \frac{\onebf\onebf^\prime}{\onebf^\prime \onebf} = \Ibf - \frac{\onebf\onebf^\prime}{n+1}
\]
the projection matrix orthogonal to $\onebf$ (i.e. into the zero-sum plane) where $\Ibf$ is the $n+1$ by $n+1$ identity matrix.  Given a set $S$ of vectors from $\reals^{n+1}$ we write $\Qbf S$  to denote the set with elements $\Qbf \sbf$ for all $\sbf \in S$, i.e. the set containing the projection of the vectors from $S$.

\begin{lemma} \label{lem:QVorZnsubsetVorAn}
The projection of $\vor(\ints^{n+1})$ into the zero-sum plane is a subset of $\vor(A_{n})$.  That is,
\[
\Qbf\vor(\ints^{n+1}) \subseteq \vor(A_{n}).
\]
\end{lemma}
\begin{IEEEproof}
Let $\ybf \in \vor(\ints^{n+1})$.  Decompose $\ybf$ into orthogonal components so that $\ybf = \Qbf \ybf + t \onebf$ for some $t \in \reals$.  Then $\Qbf\ybf \in \Qbf\vor(\ints^{n+1})$.  Assume that $\Qbf\ybf \notin \vor(A_n)$.  Then there exists some $\xbf \in A_n$ such that
\begin{align*}
\|\xbf - \Qbf\ybf\|^2 < \|\zerobf - \Qbf\ybf\|^2 & \Rightarrow \|\xbf - \ybf + t\onebf\|^2 < \|\ybf - t\onebf\|^2 \\
%& \Rightarrow \|\xbf - \ybf\|^2 + 2t(\xbf - \ybf)'\onebf + t^2\|\onebf\|^2 < \|\ybf\|^2 - 2t\ybf'\onebf + t^2\|\onebf\|^2 \\
& \Rightarrow \|\xbf - \ybf\|^2 + 2t\xbf'\onebf < \|\ybf\|^2.
\end{align*}
By definition \eqref{eq:An_sub_Zn} $\xbf'\onebf = 0$ so $\|\xbf - \ybf\|^2 < \|\ybf\|^2$.  This violates that $\ybf \in \vor(\ints^{n+1})$ and hence $\Qbf\ybf \in \vor(A_n)$.\footnote{This proof can be generalised to show that for any lattice $L$ and hyperplane $P$ such that $P\cap L$ is also a lattice it is true that $p\vor(L) \subseteq \vor(L \cap P)$ where $p$ indicates the orthogonal projection into $P$~\cite[Lemma~2.1]{McKilliam2010thesis}.}
\end{IEEEproof}

\begin{theorem}  \label{thm:VorAn=QVorZn1}
The projection of $\vor(\ints^{n+1})$ into the zero-sum plane is equal to $\vor(A_{n})$. That is,
\[
\vor(A_n) = \Qbf\vor(\ints^{n+1}).
\]
\end{theorem}
\begin{proof}
The $n$-volume of $\vor(A_n)$ is given $\sqrt{n + 1}$.  From Berger~et.~al.~\cite[Theorem 1.1]{Burger1996} we find that the $n$-volume of the projected hypercube $\Qbf\vor(\ints^{n+1})$ is equal to 
\[
\sum_{i = 1}^{n+1} \frac{\dotprod{\onebf}{\ebf_i}}{\|\onebf\|} =  \sum_{i = 1}^{n+1} \frac{1}{\sqrt{n+1}} = \sqrt{n + 1}
\] 
also. It follows from Lemma~\ref{lem:QVorZnsubsetVorAn} that $\Qbf\vor(\ints^{n+1}) \subseteq \vor(A_n)$, so, because the volumes are the same, and because $\vor(A_n)$ and $\Qbf\vor(\ints^{n+1})$ are polytopes, we have $\vor(A_n) = \Qbf\vor(\ints^{n+1})$.
\end{proof}

@@

We can make further simplifications.  Letting $t = x_1 - x_2$ and $y = x_1 + 1/2$ and changing variables gives
\[
n \sqrt{n+1} \int^{1}_{0} \int^{y}_{0}  \int^{y - 1/2}_{y - t - 1/2} \cdots \int^{y-1/2}_{y-t-1/2} \frac{f(\Qbf\xbf )}{1 - t}  dx_{n+1} \, \dots \, dx_3 \, dt \, dy,
\]
and letting $w_{i-2} = x_i - y + 1/2 + t$ for $i = 3,\dots,n+1$ gives
\begin{equation}\label{eq:intwewilluse}
n \sqrt{n+1} \int^{1}_{0} \int^{y}_{0}  \int^{t}_{0} \cdots \int^{t}_{0} \frac{f(\Qbf\xbf )}{1 - t}  dw_{n-1} \, \dots \, dw_1 \, dt \, dy.
\end{equation}
Observe that $\xbf = \wbf + (y - t - \nicefrac{1}{2})\onebf$ where $\wbf$ is the column vector
\[
\wbf = [t, 0, w_1, w_2, \dots, w_{n-1}]^\prime.
\]
Projecting orthogonal to $\onebf$ gives $\Qbf\xbf = \Qbf \wbf$.  Interestingly $\wbf$ does not contain $y$ so the term inside the integral does not depend on $y$.  This is the integral we will use to compute the moments of $A_n$.

@@

We now derive expressions for the $C_n(m)$.  Setting $f(\Qbf\xbf) = \left(\|\Qbf\wbf\|^{2}\right)^m$ in~\eqref{eq:intwewilluse} we obtain,
\[
\frac{C_m(n)}{n\sqrt{n+1}} = \int_0^1 \int_0^y \int_0^t \cdots \int_0^t \frac{\left(\|\Qbf\wbf\|^2\right)^m}{1 - t} \,dw_{n-1} \, \dots \, dw_1 \, dt \, dy.
\]
Now $\|\Qbf\wbf\|^2 = \|\wbf\|^2 - \frac{1}{n+1}(\wbf^\prime \onebf)^2$ and recalling that $\wbf = [t,0,w_1,\dots,w_{n-1}]'$ we can write
\begin{align*}
\|\Qbf\wbf\|^2 &= \|\wbf\|^2 - \frac{1}{n+1}(\wbf^\prime \onebf)^2 \\
&= t^2 + \sum_{i=1}^{n+1}w_i^2 - \frac{1}{n+1}\left( t + \sum_{i=1}^{n+1}w_i \right)^2 \\
&= t^2 + \sum_{i=1}^{n+1}w_i^2 - \frac{1}{n+1}\left( t^2 + 2 t \sum_{i=1}^{n+1}w_i + \left(\sum_{i=1}^{n+1}w_i \right)^2 \right)\\
&= C + D,
\end{align*}
say, where
\[
C = \left(\frac{n}{n+1} \right) t^2 \qquad \text{and} \qquad D = A - \frac{2t}{n+1}B - \frac{1}{n+1}B^2,
\]
and where,
\[
 A = \sum_{i=1}^{n-1}w_i^2 \qquad \text{and} \qquad B = \sum_{i=1}^{n-1}w_i.
\]
Now,
\[
 \frac{C_m(n)}{n\sqrt{n+1}} =  \int_0^1 \int_0^y \int_0^t \cdots \int_0^t \frac{(C+D)^m}{1 - t} \,dw_{n-1} \, \dots \, dw_1 \, dt \, dy,
\]
and by expanding the binomial $(C+D)^m$ we get
\[
\frac{C_m(n)}{n\sqrt{n+1}} =  \int_0^1 \int_0^y \frac{1}{1 - t}\sum_{k=0}^{m}\binom{m}{k} C^{m-k} \int_0^t \cdots \int_0^t \, D^{k} \,dw_{n-1} \, \dots \, dw_1 \, dt \, dy.
\]
Expanding $D^k$ as a trinomial gives
\begin{align*}
D^k &= \sum_{k_1+k_2+k_3=k} \frac{k! A^{k_1} B^{2k_3 + k_2}}{k_1! k_2! k_3!} \left(\frac{-1}{n+1}\right)^{k_2+k_3}2^{k_2}t^{k_2}  \\
&=  \sum_{a=0}^k\sum_{b=0}^{k-a} \frac{k!  A^{a} B^{2k - 2a - b}}{a! b! (k-a-b)!} \left(\frac{-1}{n+1}\right)^{k - a}2^{b}t^{b}
\end{align*}
where the second line follows by setting $k_1 = a$, $k_2 = b$ and $k_3 = k - a - b$.  In Appendix~\ref{sec:mult-type-integr} we show that the integral of $A^{a} B^{2k - 2a - b}$ over $w_1,\dots w_{n-1}$ is
\[
\int_0^t \cdots \int_0^t A^{a} B^{2k-2a-b} dw_{n-1} \, \dots \, dw_1 = t^{n-1+2k - b} G(n-1,a,2k - 2a - b).
\]
where $G(n,c,d)$ satisfies the recursion given by~\eqref{eq:theGrecursion}.  So, let $P$ satisfy
\begin{align*}
P &= t^{1 - n - 2k}\int_0^t \cdots \int_0^t D^k dw_{n-1} \, \dots \, dw_1 \\
&= \sum_{a=0}^k\sum_{b=0}^{k-a} \frac{2^{b} k!G(n-1,a,2k - 2a - b)}{a! b! (k-a-b)!} \left(\frac{-1}{n+1}\right)^{k - a}.
\end{align*}
Now $C^{m-k} = \left(\frac{n}{n+1} \right)^{m-k} t^{2(m-k)}$ and
\begin{align*}
\frac{C_m(n)}{n\sqrt{n+1}} &= \sum_{k=0}^{m} \binom{m}{k} \left(\frac{n}{n+1} \right)^{m-k} P \int_0^1 \int_0^y \frac{t^{n - 1 + 2m}}{1 - t} \, dt \, dy \\
&= \sum_{k=0}^{m} \binom{m}{k} \left(\frac{n}{n+1} \right)^{m-k} P \int_0^1 \beta(y,n+2m,0) dy \\
&= \frac{1}{n+2m} \sum_{k=0}^{m} \binom{m}{k} \left(\frac{n}{n+1} \right)^{m-k} P.
\end{align*}
This expression is equivalent to that from~(\ref{eq:theCmformula}).
